---
title: "Prepare performance-test norms tables for OES"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview  


The code assumes a typical RStudio project folder hierarchy, with `INPUT-FILES` and `OUTPUT-FILES` folders at the first level.

### Input Files

* single-tab, single-column, join by SS: `Percentile-Lookup-SS.csv` 
* single-tab, single-column, join by agestrat: `OES-age-labels.csv`

* multi-tab (form), single-column, join by rawscore: `GDS_lookup.xlsx`
* multi-tab (form), multi-column (scale), join by rawscore: `growth-score-lookup.xlsx`, `ageEquiv-form-lookup.xlsx`
* multi-tab (form X CI_value), multi-column (scale), join by agestrat: `Form-Agestrat-CV.xlsx`

* multi-file (form), multi-tab (agestrat), multi-column (scale), join by rawscore: `scale_lookup_interview.xlsx`, `scale_lookup_parent.xlsx`, `scale_lookup_teacher.xlsx`


Here and throughout, certain token markers are employed to designate user-input values that vary by project:  

* `{TOKEN}`: any value or series of values  
* `{FILE-PATH}`  
* `{FILE-NAME}` 

### Multi-file-tab-column lookups
The set of files `scale_lookup_interview.xlsx`, `scale_lookup_parent.xlsx`, `scale_lookup_teacher.xlsx` presents the most complex case for reading in lookup tables. The task is to lookup `SS`, and the basic operation is the many-to-one correspondence between `rawscore` and `SS`. That lookup correspondence is stratified over three levels:

1. columns (scale)
2. tabs (agestrat)
3. files (form)

<br>



###### VALID CODE TO RUN

```{r XXX, eval=FALSE}
```

###### COMMENTED SNIPPETS

```{r XXX, echo=4:8, eval=FALSE}
```
